Sample size

### 2021-05-02 scripts/r/sample-size/sample-size.Rmd
run 10 interations per n/sd combos

quantiles <- quantile(seq(lower, upper, by = 0.1), probs = seq(0, 1, 0.25),  na.rm = FALSE)
quantiles <- c(quantiles[[1]], quantiles[[2]], quantiles[[3]], quantiles[[4]], quantiles[[5]])
n_teams <- seq(15, 40, by = 5)

@@

  cat("Model:", n, sd, "\n")
  brm_model <- run_brm(data)

  sd_team <- summary(brm_model)

  return(sd_team)
}
```

@@

```{r plot}
sample_sims <- sample_sims %>%
  mutate(
    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
  )

>>>>

quantiles <- quantile(seq(lower, upper, by = 0.1), probs = seq(0, 1, 0.25),  na.rm = FALSE)
quantiles <- c(quantiles[[1]], quantiles[[2]], quantiles[[3]], quantiles[[4]], quantiles[[5]])
n_teams <- seq(5, 40, by = 5)

@@

  sd_team_i <- numeric()

  cat("Model:", n, sd, "\n")

  for (iter in 1:10) {
    cat("   Iteration", iter, "\n")
    brm_model <- run_brm(data)
    brm_summ <- summary(brm_model)
    sd_team_i <- c(sd_team_i, brm_summ$random$team[4] - brm_summ$random$team[3]) 
  }

  sd_team_mean <- mean(sd_team_i, na.rm = TRUE)
  sd_team_sd <- sd(sd_team_i, na.rm = TRUE)

  return(list(sd_team_mean, sd_team_sd))
}
```

@@

```{r plot, eval=FALSE}
sample_sims <- sample_sims %>%
  mutate(
    cri = map(sd_team, function(.x) .x$random$team[4] - .x$random$team[3]) %>% unlist()
  )
